---
title: "behavendoR_notebook_example"
author: "Lisa N. Cao"
date: "22/05/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## behavendoR

This is a template lab notebook for statistical analyses using behavendoR. We will go through the standard Watson lab workflow. 

# This is my workflow 

STAGE ONE: 
  -Preprocessing of data
    - Import data in ____ format from _________ (qualtRics)
    - Clean data using _________________
    - Create data table, clean and final version
    -
    
STAGE TWO: 
  -Data organization
  -Exploratory analysis 

STAGE THREE: 
  -Statistical Modelling 
    -Analyses I will be using are:
    -Models I have made are: 

STAGE FOUR: 
  -Visualization 
    -Basic
    -Advanced 


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
